---
title: "Assignment 2"
output: html_document
---
1. 
+  Create a for loop that finds the sum of the following vector (without using the sum() function)

```{r}
myvector <- c(1,2,3,4,5,6)
```
+  Modify this code to find the mean of the vector (don't use mean())
+  Modify your code to create two functions, one called "SumMyVector" and the other "MeanMyVector"

```{r,eval = FALSE}

SumMyVector(a)
[1] 21
MeanMyVector(a)
[1] 3.5

```

2.

+  Create a loop that will take a vector of numeric grades and create a corresponding vector containing letter grades. Base it on the following rules;<br>
100 >= A >=90, 89 >= B >= 80, 79 >= C >= 70, 69 >= D >= 60, 59 >= F <br>
It should do something like this.

```{r,eval = FALSE}
#input
NumbericGrade = c(95, 79, 92, 70) 

#Your code will produce the following vector
c("A", "C", "A", "D")

```

Use it to grade the following vector.

```{r,eval = FALSE}

grades <- c(98,49,67,23,59,78,82)

```

+  Modify your loop to be a function called "Grader"

3.

+  Create a vector x containing a sequence 1 to 100 by 0.5
+  Create a vector y equal to 2*x
+  Use the rnorm() function to add "noise" to y. Set standard deviation to 15
+  Creat a plot of y as a function of x

```{r, echo = FALSE, fig.height = 4, fig.width= 8}
par(mfrow = c(1,2))
x <- seq(1,100,1)
y <- 2*x

plot(y~x, main = "first plot")
y <- 2*x + rnorm(100, sd = 15)
plot(y~x, main = "plot with noise")
par(mfrow = c(1,1))

```

+ *BONUS*

+  Create onehundred values using the rnorm() function. Set the mean to 5 and standard deviated to 4.3. Save this vector as x
+  Save another vecotor as y and add noise using the rnorm() function
+  Plot these two vector using  plot(y~x)
+  Research the "lines" function. Add a red line to the plot that follows the data.<br>
Should look something like this.<br>
```{r,echo = FALSE, fig.height = 4, fig.width = 4}

x <- rnorm(1000, mean= 5, sd = 4.3)
y <- sin(x) + rnorm(1000)
plot(y~x)
z <- seq(-5,20,.05)
lines(z, sin(z), col = "red" )
```

4.

Write a function called pairwise.max that takes as its arguments two vectors x and y and returns a vector whose 1st element is the larger of the 1st elements of x and y, whose 2nd element is the larger of the 2nd elements of x and y, etc.

```{r}
#imagine you have these two vectors
x <- c(1,4,2,6,3,4,5)
y <- c(5,3,1,8,7,6,1)

# your code sould produce the following vector
z <- c(5,4,2,8,7,6,5)
```

5.

+ Create a for loop that runs 100 times and grows a vector where the elements of this vector are means of 100 rand uniform numbers. e.i., use mean(runif(100)).
+ Your vector will essentially be this, but use a for loop to generate it;<br><br>
c(mean(runif(100)), mean(runif(100)), mean(runif(100)), ......, mean(runif(100)))<br><br>
+ Use the hist() function to create a histogram of the vector you grew
+ Rerun this code running the loop 1000 times. Creat another histogram and comment on the difference between the two plots.<br> 
+ Create a function that reruns this code including the plot. The argument of this funtion should be how many times you would like the loops to run.
*BONUS*- Give the name of this fenomenon
