---
  title: "Assignment 3"
  date: "Due 3/10/2015"
  output: html_document
---
  </br>

## Question 1
  
Imagine someone flips a coin 100 times.</br>

You gain a dollar every time the coin comes up heads, and you lose a dollar every time it comes up tails. </br>

You start off with $50, and you want to keep track of your money over time. </br>

So you decide to create a plot showing how much money you have over time.

Can you use R to simulate this situation? (the plot and all)

### Hint: 

  This question can be done succinctly using the following commands, but complete it however you see fit: </br>
  
  ```runif()``` or ```sample()```, </br>
  ```ifelse()```, </br> 
  ```cumsum()```, </br>
  ```plot()``` </br>
  
  Your plot should look something like like this (although the data will be different every time)
  
```{r, echo= FALSE}
plot(cumsum(ifelse(runif(100)>=.5,1,-1))+50, type = 'l', ylab = "my money", xlab = "number of coins flipped")
```

### Bonus:

Make this graph twice, once using ```plot()``` and once using ggplot.
</br></br>

## Question 2
  Research the following dplyr "verbs" and give brief explanations for each.
</br></br>

 + ```select```</br>
 + ```group_by```</br>
 + ```summarize```</br>
 + ```mutate```</br>
 + ```arrange```</br>
 + ```filter```</br>
  </br></br>
  
### Bonus: 
```inner_join``` and ```outer_join```</br></br>

First describe what "join" does and then describe the difference between inner joins \& outer joins.
</br></br></br>

## Question 3
Download the ```mcd.tsv``` file from the website and put it into the directory you've been using throughout this seminar.</br>
Run the following command to load the data into R.
```{r}
mcd <- read.delim("mcd.tsv",header=TRUE,sep = "\t")
```
   a) Using this file (it's a dataset that shows McDonald's nutrition content), use dplyr to show the average calories (CAL) by food category (CATEGORY).
</br></br>
   b) Add columns for the minimum and maximum calories by category to this table. </br></br>
   c) Run the following lines of code. Describe what each of them show.
      i) ```qplot(CAL,data=mcd)```
      ii) ```qplot(CAL,SGR,data=mcd)```
      iii) ```qplot(CAL,SGR,color=CATEGORY,data=mcd)``` </br></br>
   d) Make your own interesting plot using the McDonald's dataset and ggplot.
</br></br>
  
##  Question 4 
Download the ```nba.csv``` file from the website and load it into R.</br></br>
  a) Using the NBA dataset provided, use dplyr to find the player with the highest total fouls.
</br></br>
  b) Find the average amount of points scored each season by player.
</br></br>
  c) Create a table that shows the top scoring player for each season.
</br></br>
  d) What player(s) was the top scorer for the most seasons? 
</br></br></br></br>

## Question 5 </br>
 a) Using the nycflights13 data package, use the table ```flights``` to find the average distance flown by carrier
</br></br>
 b) What data had the highest mean departure delay (dep_delay)?
</br>

### Bonus that you should really try to attempt. 
</br>
Use both the ```flights``` and ```planes``` data table to answer this. Create a table with two columns: mean distance flown and number of seats. This table will be grouped by seat. </br>

#### Hint: you will have to use a join command to join the two tables. </br></br>
